### 2019-11-12 cvpr_submission/experiments.tex
Changed table label to avoid formatting issue.

The results of these experiments are available in \Tab{tab:CoGenT_results}. 
\begin{table}[htb]
	\centering
	\noindent
	\caption{CLEVR-CoGenT accuracies for all 5 tasks when training on solely one task, jointly training on all tasks and finetuning on each task. For all experiments, the validation and test sets are identical.}\label{tab:CoGenT_results}
	\begin{adjustbox}{width=0.5\textwidth}
	\begin{tabular}{c c c c c c c }\toprule
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{Exist only} & 26.07 & 74.20	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
		\multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& 62.78	& 0.0 & 0.0 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& 77.98	& 54.08 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & 61.73 & 0.0 \\ 
		\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & 97.08 \\ 		
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

@@

Looking at the first section of \tab{tab:CoGenT_results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested. Nevertheless, we also note that a model, trained on \textit{Exist} only, obtains a score slightly better than random on \textit{CompareInteger} \& \textit{CompareAttribute}. This is due to the fact that these 3 task groups share the same labels space ('yes', 'no'). \textit{Count} and \textit{QueryAttribute} have isolated labels space (('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10') and the set of object attributes values respectively) and we thus observe an accuracy of zero for these tasks, except when trained on these.

@@

			\cmidrule(lr){1-1}
			\cmidrule(lr){2-7}
			\multicolumn{1}{ c }{\textbf{Trained on all tasks but $t$ -- Finetune on $t$ }} & &  & &  & &\\ 
			\multicolumn{1}{ c }{Exist} & 86.24 & 98.04 & 56.59 & 87.99 & 94.17 & 97.14 \\ 
			\multicolumn{1}{ c }{Count} & 46.97 & 2.80 & 78.73 & 15.60 & 35.06 & 56.60 \\
			\multicolumn{1}{ c }{CompareInteger} & 73.46 & 72.89 & 42.42 & 92.07 & 68.32 & 91.90 \\
			\multicolumn{1}{ c }{CompareAttribute} & 48.16 & 85.77 & 30.84 & 77.20 & 97.72 & 13.21 \\
			\multicolumn{1}{ c }{QueryAttribute} & 35.26 & 38.65 & 4.22 & 31.56 & 5.08 & 70.67 \\
		\bottomrule
	\end{tabular}
\end{adjustbox}
\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT_finetuning_results}
\end{table}

>>>>

The results of these experiments are available in \Tab{tab:CoGenT-results}. 
\begin{table}[htb]
	\centering
	\noindent
	\caption{CLEVR-CoGenT accuracies for all 5 tasks when training on solely one task, jointly training on all tasks and finetuning on each task. For all experiments, the validation and test sets are identical.}\label{tab:CoGenT-results}
	\begin{adjustbox}{width=0.5\textwidth}
	\begin{tabular}{c c c c c c c }\toprule
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{Exist only} & 26.07 & 74.20	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
		\multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& 62.78	& 0.0 & 0.0 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& 77.98	& 54.08 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & 61.73 & 0.0 \\ 
		\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & 97.08 \\ 		
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

@@

Looking at the first section of \tab{tab:CoGenT-results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested. Nevertheless, we also note that a model, trained on \textit{Exist} only, obtains a score slightly better than random on \textit{CompareInteger} \& \textit{CompareAttribute}. This is due to the fact that these 3 task groups share the same labels space ('yes', 'no'). \textit{Count} and \textit{QueryAttribute} have isolated labels space (('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10') and the set of object attributes values respectively) and we thus observe an accuracy of zero for these tasks, except when trained on these.

@@

			\cmidrule(lr){1-1}
			\cmidrule(lr){2-7}
			\multicolumn{1}{ c }{\textbf{Trained on all tasks but $t$ -- Finetune on $t$ }} & &  & &  & &\\ 
			\multicolumn{1}{ c }{Exist} & 86.24 & 98.04 & 56.59 & 87.99 & 94.17 & 97.14 \\ 
			\multicolumn{1}{ c }{Count} & 46.97 & 2.80 & 78.73 & 15.60 & 35.06 & 56.60 \\
			\multicolumn{1}{ c }{CompareInteger} & 73.46 & 72.89 & 42.42 & 92.07 & 68.32 & 91.90 \\
			\multicolumn{1}{ c }{CompareAttribute} & 48.16 & 85.77 & 30.84 & 77.20 & 97.72 & 13.21 \\
			\multicolumn{1}{ c }{QueryAttribute} & 35.26 & 38.65 & 4.22 & 31.56 & 5.08 & 70.67 \\
		\bottomrule
	\end{tabular}
\end{adjustbox}
\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT-finetuning-results}
\end{table}
